Fast, Scalable Phrase-Based SMT Decoding

### 2016-05-05 acl.2016/acl2016.tex
changes

This contrast with Moses where speed increases to approximately 16 threads but then actually become slower thereafter, Figure~\ref{fig:moses-speed}.
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.4]{moses-scalability.png}} 
\end{tabular}
\caption{Moses' decoding speed}
\label{fig:moses-speed}
\end{figure}

@@

We mimic the use of multi-core servers by single-threaded decoders such as mtplz~\cite{Heafield-mtplz} and Jane~\cite{peitz2012jane} by running multiple processes of the Moses decoder, each running one thread. The input is distributed to the processes using a external script.

The results in ??? shows that not only does the parallelization method scales badly even compared to Moses, it is unable to run at all when more that a certain number of threads, possibly due to higher memory requirements of running multiple memory-hungry processes, or the inefficiency of distributing work to many processes. Based on this result, single-thread decoding applications are not a viable option for efficiently utilizing the multicore servers of today.

>>>>

This contrast with Moses where speed increases to approximately 16 threads but then actually become slower thereafter, Figure~\ref{fig:moses-speed} (solid line).
\begin{figure}[h]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.5]{moses-scalability.png}} 
\end{tabular}
\caption{Moses' decoding speed}
\label{fig:moses-speed}
\end{figure}

@@

We mimic the use of multi-core servers by single-threaded decoders such as mtplz~\cite{Heafield-mtplz} and Jane~\cite{peitz2012jane} by running multiple processes of the Moses decoder, each running one thread. The input is distributed to the processes using a external script. The result in Figure~\ref{fig:moses-speed} (dashed line) shows that this method scales much better than multithreading the application.
